\documentclass{article}
\usepackage{bubblecv}

\begin{document}


\begin{cv}[avatar]{Giorgia Savo}{Secret Agent}


\cvsection[summary]{Profilo}  %-----------------------------------------------------------

Highly skilled secret agent with a license to kill. 
Bringing together outstanding combat and intelligence abilities with a charismatic and persuasive personality. 
A dedicated and adaptable professional committed to global security.


\cvsection[work]{Esperienze Lavorative}  %------------------------------------------------------

\begin{cvevent}[1962][present]
    \cvname{Secret Agent}
    \cvdescription{MI6 Intelligence Agency, London}
    \begin{itemize}
        \item Covert intelligence operations for national security.
        \item Infiltration from high-risk environments.
        \item Utilization of advanced espionage techniques and gadgets.
        \item Surveillance, analysis, and threat prevention.
    \end{itemize}
\end{cvevent}


\cvsection[education]{Formazione}  %------------------------------------------------------

\begin{cvevent}[1958][09-2023]
    \cvname{Laurea Triennale in Lingue Orientali - L??}
    \cvdescription{MI6 Training Facility, London}
    \textbf{Courses and Achievements:}
    \begin{itemize}
        \item Mastered advanced techniques for discreetly gathering intelligence and conducting covert operations.
        \item Trained extensively in planning and executing covert operations and infiltrating high-security areas.
        \item Received rigorous combat training in martial arts, firearms handling, and tactical skills.
        \item Proficient in surveillance methods, counter-surveillance techniques, and analyzing gathered intelligence.
    \end{itemize}
\end{cvevent}


\cvsection[target]{Missions}  %----------------------------------------------------------

\begin{cvevent}[2002]
    \cvname{Die Another Day}
    Uncovered a North Korean general's plan to use a satellite weapon to create a war between North and South Korea.
\end{cvevent}

\cvseparator[2]
\begin{cvevent}[1999]
    \cvname{The World Is Not Enough}
    Protected an oil heiress from a terrorist plotting to exploit her family's resources and trigger a global meltdown.
\end{cvevent}

\cvseparator[2]
\begin{cvevent}[1997]
    \cvname{Tomorrow Never Dies}
    Investigated a media mogul's plot to provoke a war between the UK and China for increased ratings and power.
\end{cvevent}

\cvseparator[2]
\begin{cvevent}[1995]
    \cvname{GoldenEye}
    Prevented the use of the GoldenEye satellite weapon system by a rogue agent to cause global financial chaos.
\end{cvevent}


\cvsidebar %-----------------------------------------------------------------------------


\cvsection[contact]{Contact}  %----------------------------------------------------------

\begin{cvitem}[Envelope][4]
    \textbf{Email}\\
    \href{mailto:}{\texttt{james.bond@mi6.gov}}
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Phone][4]
    \textbf{Phone}\\
    \href{tel:+393319783436}{\texttt{+39 331 978 3436}}
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Home][4]
    \textbf{Address}\\
    Via\\ London, United Kingdom
\end{cvitem}

\cvsection[skills]{Skills}  %-----------------------------------------------------------

\begin{cvitem}
    Espionage Techniques
\end{cvitem}

\cvseparator
\begin{cvitem}
    Surveillance
\end{cvitem}

\cvseparator
\begin{cvitem}
    Combat Training
\end{cvitem}

\cvseparator
\begin{cvitem}
    Infiltration
\end{cvitem}

\cvseparator
\begin{cvitem}
    Problem Solving
\end{cvitem}

\cvseparator
\begin{cvitem}
    Effective Communication
\end{cvitem}

\cvseparator
\begin{cvitem}
    Adaptability
\end{cvitem}

\cvseparator
\begin{cvitem}
    Teamwork
\end{cvitem}


\cvsection[languages]{Languages}  %--------------------------------------------------------

\cvskill{Italiano}{Fluent}{1.0}
\cvskill{Inglese}{Fluent}{0.9}
\cvskill{Spagnolo}{Intermediate}{0.6}
\cvskill{Coreano}{Basic}{0.3}
\cvskill{Cinese}{Basic}{0.3}

\end{cv}

\cvfootnote{
    \tiny Autorizzo il trattamento dei miei dati personali, ai sensi del D. lgs. 196 del 30 giugno 2003
}

\end{document}